# Regression and Model Validation

*Describe the work you have done this week and summarize your learning.*

- Describe your work and results clearly. 
- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods.
- Assume the reader has no previous knowledge of your data or the more advanced methods you are using.

The present chapter explores the dataset from the International Survey of Approaches to Learning. The data uses several variables to measure learning strategies and approaches, understanding and attitute of people towards statistics. This data will be further explained as we move forward in this chapter
```{r}
date()
```

# Chapter 2: Regression and Model Validation

The present chapter explores the dataset from the International Survey of Approaches to Learning. The data uses several variables to measure learning strategies and approaches, understanding and attitute of people towards statistics. This data will be further explained as we move forward in this chapter

## **Part 1: Data Wrangling**
## Reading data

Reading the table from the web
read.table()only allows us to read the data. To be able to make changes to it, we need to store it in R. For this, we save it by the name "learn"

```{r}
options(repos = list(CRAN="http://cran.rstudio.com/"))
install.packages("DT")
learn <- read.table("http://www.helsinki.fi/~kvehkala/JYTmooc/JYTOPKYS3-data.txt", sep="\t", header=TRUE)
DT::datatable(learn, options = list(pageLength = 20))
# the DT package helps limit the table view to 20 rows at a time - it is a pretty large dataset
```



## Dimension and Structure of the dataset

### Dimensions of "learn"

```{r}

dim(learn)


#The table "learn" has 183 rows and 60 columns. However, this is also mentioned right below the table.
```
### Looking at the structure
```{r}
str(learn)

# All variables of integer type, except for gender, which is a character type
```

## Creating an Analysis dataset

As previosly mentioned,this dataset records variables to assess learning, understanding and attitudes of people towards statistics. The next steps take a look at some of these variables, namely

* Attitude: Global attitude toward statistics

* Deep: Deep approach to learning, which involves gaining an in-depth understanding

* Surf: Surface approach, consisting primarily of memorizing without understanding

* Stra: Strategic approach, which students apply in the face of constraints such as deadlines and syllabus


### 1. Scaling vectors to their original values:


Now, to create an analysis dataset, we need to keep in mind that some parameters are aggregates of two or more variables. These are:

1. Attitude = Da + Db + Dc + Dd + De + Df + Dg + Dh + Di + Dj

2. **Deep = d_sm + d_ri + d_ue**, and
  
  + d_sm = D03 + D11 + D19 + D27
  
  + d_ri = D07 + D14 + D22 + D30
  
  + d_ue = D06 + D15 + D23 + D31

3. **Stra = st_os + st_tm**, where

  + st_os = ST01 + ST09 + ST17 + ST25
  
  + st_tm = ST04 + ST12 + ST20 + ST28

4. **Surf = su_lp + su_um + su_sb**, where

  + su_lp = SU02 + SU10 + SU18 + SU26
  
  + su_um = SU05 + SU13 + SU21 + SU29
  
  + su_sb = SU08 + SU16 + SU24 + SU32

In order to **scale** Attitude, we need to divide it by the number of variables that constitute it.This is easily done by creating a new variable and assigning the new value to it

Hence,

```{r}

# divide each number in the column "Attitude" by 10

# create column 'attitude' by scaling the column "Attitude"
learn$attitude <- learn$Attitude / 10

```
Now for the other variables, since "deep", "Surf" and "stra" do not exist in this dataset, we must create them by aggregating and averaging their constituents

*But first, lemme access the dplyr library*

```{r}
library(dplyr)
# questions related to deep, surface and strategic learning
deep_questions <- c("D03", "D11", "D19", "D27", "D07", "D14", "D22", "D30","D06",  "D15", "D23", "D31")
surface_questions <- c("SU02","SU10","SU18","SU26", "SU05","SU13","SU21","SU29","SU08","SU16","SU24","SU32")
strategic_questions <- c("ST01","ST09","ST17","ST25","ST04","ST12","ST20","ST28")

# select the columns related to deep learning 
deep_columns <- select(learn, one_of(deep_questions))
# and create column 'deep' by averaging
learn$deep <- rowMeans(deep_columns)

# select the columns related to surface learning 
surface_columns <- select(learn, one_of(surface_questions))
# and create column 'surf' by averaging
learn$surf <- rowMeans(surface_columns)

# select the columns related to strategic learning 
strategic_columns <- select(learn, one_of(strategic_questions))
# and create column 'stra' by averaging
learn$stra <- rowMeans(strategic_columns)
# and create column 'stra' by averaging


```
Now these columns can be extracted from the original table and made into a table of their own, as it makes working with the data easier.

```{r, echo=FALSE}
# Pre-exercise-code (Run this code chunk first! Do NOT edit it.)

# Click the green arrow ("Run Current Chunk") in the upper-right corner of this chunk. This will initialize the R objects needed in the exercise. Then move to Instructions of the exercise to start working.

learn <- read.table("http://www.helsinki.fi/~kvehkala/JYTmooc/JYTOPKYS3-data.txt", sep="\t", header=TRUE)
learn$attitude <- learn$Attitude / 10
deep_questions <- c("D03", "D11", "D19", "D27", "D07", "D14", "D22", "D30","D06",  "D15", "D23", "D31")
learn$deep <- rowMeans(learn[, deep_questions])
surface_questions <- c("SU02","SU10","SU18","SU26", "SU05","SU13","SU21","SU29","SU08","SU16","SU24","SU32")
learn$surf <- rowMeans(learn[, surface_questions])
strategic_questions <- c("ST01","ST09","ST17","ST25","ST04","ST12","ST20","ST28")
learn$stra <- rowMeans(learn[, strategic_questions])
keep_columns <- c("gender","Age","attitude", "deep", "stra", "surf", "Points")

# select the 'keep_columns' to create a new dataset
learn_an <- keep_columns
learn_an

```

```{r}
# veiw the columns
learn$deep
learn$surf
learn$stra
```

### Choosing the columns we will be using for our analysis, and creating a subset:

```{r}
library(dplyr)

# The subset function appears to have worked better for me, rather than selecting columns as explained in exercise 2

## We call this new subset "learn_an" (an=analysis)

learn_an <- subset(learn, select = c("gender","Age","attitude", "deep", "stra", "surf", "Points"))

DT::datatable(learn_an, options = list(pageLength = 20))


```
### Excluding zeroes from our new subset

Zeroes in the column "Points" represent students not taking the exam, so these observations will not be used in our analysis. 

```{r}
# We create another subset called "analysis", which excludes all rows where the value for Points is 0.

analysis<-subset(learn_an, Points!="0")

dim(analysis)

#  Our new dataset "analysis" has 166 observations for 7 variables now. This is the data we will be using for our analyses
DT::datatable(analysis, options = list(pageLength = 20))
```
## Exporting the data

```{r}
# Set working directory to a local file on the device so the data may be saved and read from there

setwd("C:/Users/Megha Khanduri/OneDrive/Desktop/maximum effort/ELP Ganga Basin/courses/IODS/IODS-project/data")
```
Exporting the data as a csv file requires the writecsv function, for which readr library must be accessed. Therefore,
```{r}
library(readr)

write.csv(analysis, file = "learning2014.csv")

```
Let's see if it worked, and if the file can be read.
```{r}
learning2014 <- read_csv("C:/Users/Megha Khanduri/OneDrive/Desktop/maximum effort/ELP Ganga Basin/courses/IODS/IODS-project/learning2014.csv")
DT::datatable(learning2014, options = list(pageLength = 20))
```
Let's see if the structure of this dataset is correct
```{r}
str(learning2014)

head(learning2014)
```
**This concludes the data wrangling section of the chapter. Next, we will move to analysing the data.**
